Machine Learning guided workflow for Ribosome Binding Site engineering

### 2021-05-14 paper/methods.tex
Updated Results in Paper.
add challenges in result sec
Updates from Overleaf

The flowchart of machine learning based experimental design is shown in Figure \ref{fig: Flowchart}. 
To automatically design the RBS sequences in batch using machine learning, we can logically divided the workflow into two parts: 
1) \textbf{LEARN}: A regression algorithm which takes the RBS sequences as input features and TIR scores as labels, trains on sequences with known labels and returns the predicted TIR scores and the respective confidence intervals. 
2) \textbf{DESIGN}: An online learning approach which recommends the RBS sequences based on the predicted TIR scores and confidence intervals.

\subsubsection{LEARN: Gaussian Process Regression with String Kernel}

@@

\subsubsection{DESIGN: Batch UCB}

>>>>

The flowchart of machine learning based experimental design is shown in Figure \ref{fig: Flowchart}. 
To automatically design the RBS sequences in batch using machine learning, we can logically divided the workflow into two parts: 
1) \textbf{LEARN}: A regression algorithm which takes the RBS sequences as input features and TIR scores as labels, trains on sequences with known labels and returns the predicted TIR scores and the respective confidence intervals.
2) \textbf{DESIGN}: An online learning approach which recommends the RBS sequences based on the predicted TIR scores and confidence intervals.
The implementation of the machine learning algorithm is in Python 3.7 and scikit-learn library \cite{scikit-learn}.

\subsubsection{Prediction: Gaussian Process Regression with String Kernel}

@@

\subsubsection{Recommendation: Batch Upper Confidence Bound Bandit}
